Turned on!": Momentum in Round-Based First Person Shooter Esports

### 2022-07-18 presentation.qmd
add state graph

>>>>

```{r}
#| label: p_filt_val_o_series_win_prop_over_expected
filt_val_o_win_prop <- val_o_win_prop |> 
  filter(
    pre_cumu_w >= 3, pre_cumu_l >= 3
  )
filt_val_max_diff_win_series_prop <- max(abs(filt_val_o_win_prop$diff_win_series_prop))
p_filt_val_o_series_win_prop_over_expected <- filt_val_o_win_prop |> 
  ggplot() +
  common_val_heatmap_layers() +
  heatmap_tile(
    .fill = 'diff_win_series_prop'
  ) +
  heatmap_text_layers(
    .df = filt_val_o_win_prop, 
    .f = o_series_win_over_expected_text_layer,
    .threshold = 0.1,
    .labeller = val_heatmap_div_labeller
  ) +
  scale_fill_gradient2(
    low = extract_ggsci_mid_color('brown'),
    high = extract_ggsci_mid_color('cyan'),
    mid = 'white',
    limits = c(
      -filt_val_max_diff_win_series_prop,
      +filt_val_max_diff_win_series_prop
    ),
    midpoint = 0
  ) +
  labs(
    title = 'Offensive Series Win % Over Expected'
  )
p_filt_val_o_series_win_prop_over_expected
save_for_slide(p_val_o_series_win_prop_over_expected)
```
